Analysis for Project

### 2021-11-11 analysis/analysis.Rmd
Add plot_effect_point function
Instead of using a scatterplot, this function creates a dot plot panelized by multiracial groups. I think it is far easier to understand than the scatterplots.

>>>>

```{r}
plot_effect_point <- function(model) {

  #ok convert this to have single race groups for each multiracial group
  #panel and get the assumed midpoint value
  coef_table <- map(as.list(str_subset(coefs$term, "/")), function(x) {
    coefs %>%
      filter(term %in% c(x, str_split(x, "/")[[1]])) %>%
      mutate(mrace=factor(x,
                          levels=c("Black/White",
                                   "White/Indigenous",
                                   "Latino/Asian",
                                   "Black/Latino",
                                   "White/Latino",
                                   "Indigenous/Latino",
                                   "Black/Asian",
                                   "White/Asian",
                                   "Indigenous/Asian",
                                   "Black/Indigenous")),
             estimate_mid=ifelse(multiracial, 
                                 mean(estimate[!multiracial]),
                                 estimate),
             estimate=ifelse(multiracial, estimate_mid+estimate,
                             estimate))
  }) %>%
    bind_rows()

  # I want term to be ordered so that multiracial groups are always between two
  # constituent monoracial groups and monoracial groups to be sorted by the 
  # magnitude of the estimate option. This is complicated but I should be able
  # to do this by inserting multiracial groups immediately below the higher 
  # of the two groups

  #get terms ordered
  race_names <- levels(reorder(factor(coef_table$term), coef_table$estimate))
  #pull out single race and multiple race as separate vectors
  race_single <- str_subset(race_names, "/", negate=TRUE)
  race_multi <- str_subset(race_names, "/", negate=FALSE)
  #start with single races
  race_full <- race_single
  #now loop through multiple race names and append based on the higher group
  for(race in race_multi) {
    temp <- str_split(race, "/")[[1]]
    idx <- max(which(race_full==temp[1]), which(race_full==temp[2]))
    race_full <- append(race_full, race, idx-1)
  }

  #now use this as the levels of term as a factor
  coef_table <- coef_table %>%
    mutate(term=factor(term, levels=race_full))

  ggplot(coef_table, aes(x=term, y=estimate,
                         color=multiracial,
                         ymin=estimate-1.96*std.error,
                         ymax=estimate+1.96*std.error))+
    geom_hline(aes(yintercept=estimate_mid, linetype=multiracial), 
               color="grey80")+
    geom_linerange(alpha=0.5)+
    geom_point()+
    coord_flip()+
    facet_wrap(~mrace, ncol=3, scales="free_y")+
    theme_bw()+
    theme(legend.position = "none", panel.grid = element_blank())+
    scale_color_manual(values=c("grey40","black"))+
    scale_linetype_manual(values=c(3,1))+
    labs(x=NULL,
         y="actual log odds ratio of grade retenion")
}
```
